---
title: 'Field Mapping of Knowledge Structure'
author: "Daniel S. Hain"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    toc: no
    toc_depth: '3'
    df_print: paged
  html_notebook:
    theme: flatly
    code_folding: hide
    df_print: paged
    number_sections: yes
    toc: no
    toc_depth: 3
    toc_float:
      collapsed: no
params:
  institute:
    value: null
  department:
    value: null
---

<!---
# Add to YAML when compiling html --< when reviewing change first line to: html_notebook
  html_document:
    theme: flatly
    code_folding: hide
    df_print: paged
    number_sections: true
    toc: false
    toc_depth: 3
    toc_float:
      collapsed: false

# Add when compiling pdf
# Add to YAML when compiling html
   bookdown::pdf_document2: 
    fig_caption: true
    number_sections: true
    global_numbering: true
--->


```{=html}
<style type="text/css">
.main-container {
  max-width: 1200px;
  margin-left: auto;
  margin-right: auto;
}
</style>
```

```{r setup, include=FALSE}
### Generic preamble
#rm(list=ls())
Sys.setenv(LANG = "en")
options(scipen = 5)

set.seed(1337)

### Load packages  
# general
library(tidyverse)
library(magrittr)
library(widyr)

# Kiblio & NW
library(bibliometrix)
library(tidygraph)
library(ggraph)
library(igraph)

# NLP
library(tidytext)

# Dataviz
library(plotly)
library(ggforce)
library(ggrepel)
library(patchwork)

# Knit
library(knitr) # For display of the markdown
library(kableExtra) # For table styling

# own functions
source("../functions/functions_basic.R")
source("../functions/functions_summary.R")
source("../functions/00_parameters.R")

# Knitr options
knitr::opts_chunk$set(echo = FALSE, 
                      warning = FALSE, 
                      message = FALSE)
```

<!-- ####################################################################################### -->
<!-- ####################################################################################### -->
<!-- ############################# NEXT PART ############################################### -->
<!-- ####################################################################################### -->
<!-- ####################################################################################### -->

```{r, include=FALSE}
# When doing it here in the notebook
var_inst <- 'AI'
var_dept <- 'v1'
var_label <- 'AI, industry and innovation dynamics'

# When calling from a highert level script
#var_inst <- params$institute
#var_dept <- params$department
```

# Introduction: Mapping of broad research field around `r var_label`

Here are preliminary results of the bibliometric mapping of the research field. Its purpose is:

* To map the broader research community and distinct research field the department contributes to.
* Identify core knowledge bases, research areas trends and topics.
* Highlight the positioning of the department within this dynamics.

The method for the research-field-mapping can be reviewed here:

[Rakas, M., & Hain, D. S. (2019). The state of innovation system research: What happens beneath the surface?. Research Policy, 48(9), 103787.](https://doi.org/10.1016/j.respol.2019.04.011)

**Note:** The analysis in this document depicts the *larger research field* around the department, thereby all analysis results are based on the publications of the department plus related.

## Seed articles

* The methodology takes a set of self-selected seed articles as point of departure. 
* For every of these seed articles, the 2000 articles with the highest bibliographic coupling are extracted.
' They jointly represent the larger research field.
* The following seedds are used in this analysis

```{r}
convert2df(file = '../data/scopus_00.csv', dbsource = "scopus", format = "csv") %>% as_tibble() %>% select(AU, PY, TI, SO)
```

<!-- ####################################################################################### -->
<!-- ####################################################################################### -->
<!-- ############################# NEXT PART ############################################### -->
<!-- ####################################################################################### -->
<!-- ####################################################################################### -->

```{r, include=FALSE}
# Load data
M <- readRDS(paste0('../../temp/M_', str_to_lower(var_inst), '_', str_to_lower(var_dept), '.rds')) %>% as_tibble() %>% 
  distinct(UT, .keep_all = TRUE) %>% 
  filter(PY >= PY_min, PY <= PY_max) %>%
  group_by(PY) %>%
    mutate(TC_cohort_rank = percent_rank(TC)) %>%
  ungroup() 
```

```{r}
#com_labels <- tibble(com = NA, label = NA, type = NA)

com_labels <- read_csv2('../data/community_labeling.csv') %>% 
  arrange(com) %>%
  #filter(institute == var_inst, department == var_dept) %>% arrange(institute, department, type, com) %>%
  mutate(label = ifelse(is.na(label), paste0(type, ' ', com, ': unlabeled'), paste0(type, ' ', com, ': ', label)))
```

# General Overview over the research field

**Note:** This section provides basic descriptives of th identified research fielld, including number of articles over time, countries, institutions, and authors. See `Technical description`for additional explanations.

```{r, include=FALSE}
# results <- biblioAnalysis(M, sep = ";")
results <- read_rds(paste0('../../temp/M_res_', str_to_lower(var_inst), '_', str_to_lower(var_dept), '.rds'))
```

## Main Indicators: Publications, Authors, Countries 

```{r}
results %>% summary()
```

```{r}
#prod_AU <- M %>% authorProdOverTime(k = 10, graph = TRUE)
#plot(prod_AU$graph)
```

```{r, include=FALSE}
rm(results, prod_AU)
```

## Main institutions, journals, keywords

```{r, fig.width=17.5, fig.height=17.5}
# # institutions, keywords, citations
M_threefield <- readRDS(paste0('../../temp/threefield_', str_to_lower(var_inst), '_', str_to_lower(var_dept), '.rds')) 
M_threefield
```


<!-- ####################################################################################### -->
<!-- ####################################################################################### -->
<!-- ############################# NEXT PART ############################################### -->
<!-- ####################################################################################### -->
<!-- ####################################################################################### -->

# Topic modelling 

**Note:** Here, we report the results of a BERTYopic topic-modelling (basically, clustering on words) on all title+abstract texts. Identified topics can be interpreted as broad themes in the research field. See `Technical description`for additional explanations.

```{r, include=FALSE}
M_top <- readRDS(paste0('../../temp/M_top_', str_to_lower(var_inst), '_', str_to_lower(var_dept), '.rds'))
```

```{r, include=FALSE}
com_names_top <- tibble( 
  com = 1:(M_top %>% pull(com) %>% n_distinct()),
  type = 'TP',
  col = com %>% gg_color_select(pal = pal_tp)) %>%
  left_join(com_labels %>% filter(type == 'TP') %>% select(com, label), by = 'com') %>%
  mutate(label = ifelse(is.na(label), paste0('TP ', com, ': unlabeled'), label))
            
# # 1st alternative: Number them 1-n
# paste(type, 1:(text_lda_gamma %>% pull(topic) %>% n_distinct()))           
```

```{r, include=FALSE}
M_top %<>%  inner_join(com_names_top %>% select(com, label, col), by = 'com')
```

```{r, fig.width = 15, fig.height=7.5}
M_top %>%
  mutate(PY = as.numeric(PY)) %>%
  count(PY, label, name = 'weight') %>%
  group_by(PY) %>% mutate(weight_PY = sum(weight)) %>% ungroup() %>%
  mutate(weight_rel = weight / weight_PY) %>%
  select(PY, label, weight, weight_rel) %>%
  filter(PY >= PY_min & PY <= PY_max) %>%
  arrange(PY, label) %>%
  plot_summary_timeline(y1 = weight, y2 = weight_rel, t = PY, t_min = PY_min, t_max = PY_max, by = label,  label = TRUE, pal = pal_tp, 
                        y1_text = "Topic popularity annualy", y2_text = "Share of topic annually") +
  plot_annotation(title = paste('Topic Modelling:', var_inst, 'Field around', var_dept, sep = ' '),
                  subtitle = paste('Timeframe:', PY_min, '-', PY_max , sep = ' '),
                  caption = 'Absolute topic appearance (left), Relative topic appearance (right)')
```

## Automated (LMM) summary 

Works a bit less precise, since it only has titles and no abstracts

```{r}
com_labels_TP <- com_labels %>% filter(type == 'TP') %>%
  mutate(label = label %>% str_replace('&', 'and')) %>%
  mutate(description = 	description %>% str_replace('&', 'and'))

for (i in 1:nrow(com_labels_TP)) {#i=1
  com_labels_n <- com_labels_TP[i,]
  writeLines(paste('Label:', com_labels_n$label, ' \n ',
        'Description:', com_labels_n$description, ' \n \n ',
        collapse = ' '))
}
```

<!-- ####################################################################################### -->
<!-- ####################################################################################### -->
<!-- ############################# NEXT PART ############################################### -->
<!-- ####################################################################################### -->
<!-- ####################################################################################### -->

# Knowledge Bases: Co-Citation network analysis 

**Note:** This analysis refers the co-citation analysis, where the cited references and not the original publications are the unit of analysis. Identified knowledge bases can be interpreted as the knowledge foundation the field draws from. See `Technical description`for additional explanations.

```{r, include=FALSE}
C_nw <- readRDS(paste0('../../temp/C_nw_', str_to_lower(var_inst), '_', str_to_lower(var_dept), '.rds'))  %>%
  drop_na(com)
```

```{r, include=FALSE}
com_names_cit <- tibble( 
  com = 1:(C_nw %>% pull(com) %>% n_distinct()),
  type = 'KB',
  col = com %>% gg_color_select(pal = pal_kb)) %>%
  left_join(com_labels %>% filter(type == 'KB') %>% select(com, label), by = 'com') %>%
  mutate(label = ifelse(is.na(label), paste0('KB ', com, ': unlabeled'), label))

# # 1st alternative: Number them 1-n
# paste(type, 1:(C_nw %>% pull(com) %>% n_distinct()))
```

```{r, include=FALSE}
C_nw %<>% left_join(com_names_cit %>% select(com, label, col), by = "com")
```

## Development

```{r, include=FALSE}
el_2m <- readRDS(paste0('../../temp/el_2m_', str_to_lower(var_inst), '_', str_to_lower(var_dept), '.rds')) %>%
  drop_na()
```


```{r, include=FALSE}
cit_com_year <- el_2m %>%
  count(com_cit, PY, name = 'TC') %>%
  group_by(PY) %>%
  mutate(TC_rel = TC / sum(TC)) %>%
  ungroup() %>%
  arrange(PY, com_cit) %>%
  left_join(com_names_cit , by = c('com_cit' = 'com')) %>% 
  complete(label, PY, fill = list(TC = 0, TC_rel = 0))
```

```{r, fig.width = 15, fig.height=7.5}
cit_com_year %>%
  plot_summary_timeline(y1 = TC, y2 = TC_rel, t = PY, t_min = PY_min, t_max = PY_max, by = label, pal = pal_kb, label = TRUE,
                        y1_text = "Number citations recieved annually",  y2_text = "Share of citations recieved annually") +
  plot_annotation(title = paste('Knowledge Bases:', var_inst, 'Field around Dept.', var_dept, sep = ' '),
                  subtitle = paste('Timeframe:', PY_min, '-', PY_max , sep = ' '),
                  caption = 'Absolute knowledge base appearance (left), Relative knowledge base appearance (right)')
```

## Publications per cluster

```{r, include=FALSE}
kb_stats <- C_nw %>%
  group_by(label) %>%
  summarise(n = n(), density_int = ((sum(dgr_int) / (n() * (n() - 1))) * 100) %>% round(3)) %>%
  relocate(label, everything())
```

```{r}
kb_sum <-C_nw %>% group_by(com) %>% 
  arrange(com, desc(dgr_int)) %>%
  mutate(name = name %>% str_trunc(150)) %>%
  slice_max(order_by = dgr_int, n = 10, with_ties = FALSE) %>% 
  ungroup() %>%
  select( name, dgr_int, dgr) %>%
  kable() 

for(i in 1:nrow(com_names_cit)){
  kb_sum <- kb_sum %>%
    pack_rows(paste0('Knowledge Base ', i, ': ', com_names_cit[i, 'label'],
                     '   (n = ', kb_stats[i, 'n'], ', density =', kb_stats[i, 'density_int'] %>% round(2), ')' ), 
              (i*10-9),  (i*10), label_row_css = "background-color: #666; color: #fff;") 
  }

kb_sum %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), font_size = 10)
```

## Automated (LMM) summary 

Works a bit less precise, since it only has titles and no abstracts

```{r}
com_labels_KB <- com_labels %>% filter(type == 'KB') %>%
  mutate(label = label %>% str_replace('&', 'and')) %>%
  mutate(description = 	description %>% str_replace('&', 'and'))

for (i in 1:nrow(com_labels_KB)) {#i=1
  com_labels_n <- com_labels_KB[i,]
  writeLines(paste('Label:', com_labels_n$label, ' \n ',
        'Description:', com_labels_n$description, ' \n \n ',
        collapse = ' '))
}
```

<!-- ####################################################################################### -->
<!-- ####################################################################################### -->
<!-- ############################# NEXT PART ############################################### -->
<!-- ####################################################################################### -->
<!-- ####################################################################################### -->

# Research Areas: Bibliographic coupling analysis

**Note:** This analysis refers the bibliographic coupling analysis, where original publications are the unit of analysis. Identified research areas can be interpreted as the field's current research frontier. See `Technical description`for additional explanations.

## Development

```{r, include=FALSE}
M_bib <- readRDS(paste0('../../temp/M_bib_', str_to_lower(var_inst), '_', str_to_lower(var_dept), '.rds')) %>% 
  as_tibble() %>%
  drop_na(com)
```

```{r, include=FALSE}
com_names_bib <- tibble( 
  com = 1:(M_bib %>% pull(com) %>% n_distinct()),
  type = 'RA',
  col = com %>% gg_color_select(pal = pal_ra)) %>%
  left_join(com_labels %>% filter(type == 'RA') %>% select(com, label), by = 'com') %>%
  mutate(label = ifelse(is.na(label), paste0('RA ', com, ': unlabeled'), label))

# # 1st alternative: Number them 1-n
# paste(type, 1:(M_bib %>% pull(com) %>% n_distinct()))
```

```{r, include=FALSE}
M_bib %<>% left_join(com_names_bib %>% select(com, label, col), by = "com")
```

```{r, fig.width = 15, fig.height=7.5}
M_bib %>%
  mutate(PY = PY %>% as.numeric()) %>%
  group_by(label, PY) %>% summarise(n = n()) %>% ungroup() %>%
  group_by(PY) %>% mutate(n_PY = sum(n)) %>% ungroup() %>%
  mutate(n_rel = n / n_PY) %>%
  select(label, PY, n, n_rel) %>%
  arrange(label, PY) %>% 
  complete(label, PY, fill = list(n = 0, n_rel = 0)) %>%
  plot_summary_timeline(y1 = n, y2 = n_rel, t = PY, t_min = PY_min, t_max = PY_max, by = label, label = TRUE, pal = pal_ra,
                        y1_text = "Number publications annually", y2_text = "Share of publications annually") +
  plot_annotation(title = paste('Research Areas:', var_inst, 'Field around Dept.', var_dept, sep = ' '),
                  subtitle = paste('Timeframe:', PY_min, '-', PY_max , sep = ' '),
                  caption = 'Absolute research area appearance (left), Relative research area appearance (right)')
```

## Publications by cluster

```{r, include=FALSE}
ra_stats <- M_bib %>%
  drop_na(com) %>%
  group_by(com, label) %>%
  summarise(n = n(), density_int = ((sum(dgr_int) / (n() * (n() - 1))) * 100) %>% round(3)) %>%
  select(com, label, everything())
```

```{r}
ra_sum <- M_bib %>% 
  left_join(M %>% select(UT, AU, TI, TC, DI), by = 'UT') %>%
  group_by(label) %>% 
  mutate(dgr_select = (dgr_int / max(dgr_int) * (TC / max(TC))) ) %>%
  slice_max(order_by = dgr_select, n = 10, with_ties = FALSE) %>% 
  mutate(TC_year = (TC / (2021 + 1 - PY)) %>% round(2),
         dgr_int = dgr_int %>% round(2),
         AU = AU %>% str_trunc(25),
         TI = TI %>% str_trunc(125) %>% paste0("[", . , "](https://doi.org/", DI, ")")) %>%
  ungroup() %>%
  select(AU, PY, TI, dgr_int, TC, TC_year) %>%
  kable()


for(i in 1:nrow(com_names_bib)){
  ra_sum  %<>%
    pack_rows(paste0('Research Area ', i, ': ', com_names_bib[i, 'label'],
                     '   (n = ', ra_stats[i, 'n'], ', density =', ra_stats[i, 'density_int'] %>% round(2), ')' ), 
              (i*10-9),  (i*10), label_row_css = "background-color: #666; color: #fff;") 
  }

ra_sum %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), font_size = 10)
```

## Automated (LMM) summary 

```{r}
com_labels_RA <- com_labels %>% filter(type == 'RA') %>%
  mutate(label = label %>% str_replace('&', 'and')) %>%
  mutate(description = 	description %>% str_replace('&', 'and'))

for (i in 1:nrow(com_labels_RA)) {#i=1
  com_labels_n <- com_labels_RA[i,]
  writeLines(paste('Label:', com_labels_n$label, ' \n ',
        'Description:', com_labels_n$description, ' \n \n ',
        collapse = ' '))
}
```

## Further Analysis

```{r, include=FALSE}
g_agg <- readRDS(paste0('../../temp/g_bib_agg_', str_to_lower(var_inst), '_', str_to_lower(var_dept), '.rds')) %N>%
  arrange(com) # %>%
#   mutate(name = names_ra %>% pull(com_ra_name),
#          color = cols_ra)
```

```{r, fig.height= 7.5, fig.width=7.5}
g_agg %E>% 
  filter(weight > 0 & from != to) %>%
  filter(weight >= quantile(weight, 0.25) )  %N>%
  mutate(com = com_names_bib %>% pull(label)) %>%
  ggraph(layout = "circle") + 
  geom_edge_fan(strenght = 0.8, aes(width = weight), alpha = 0.2)  + 
  geom_node_point(aes(size = N, color = com))  + 
  geom_node_text(aes(label = com), repel = TRUE) +
  #theme_graph(base_family = "Arial") +
  theme(legend.position = 'bottom') +
  scale_size(range = c(2,20)) +
  scale_color_brewer(palette = pal_ra) +
  labs(title = paste('Research Area Connectivity:', var_inst, 'Field around Dept.', var_dept, sep = ' '),
                  subtitle = paste('Timeframe:', PY_min, '-', PY_max , sep = ' '),
                  caption = 'Nodes = Identified Research Areas; Edges: Bibliographic coupling strenght (Jaccard weighted)')
```

# Overal interplay

## Knowledge Bases, Research Areas & Topics Interaction

```{r, include=FALSE}
# Nodes
nl_3m <- com_names_bib %>%
  bind_rows(com_names_cit) %>%
  bind_rows(com_names_top) %>%
  rename(name = label,
         com_nr = com) %>%
  relocate(name)

# Edges
el_2m_kb <- el_2m %>%
  select(-from, -to) %>%
  inner_join(com_names_cit %>% select(com, label), by = c('com_cit' = 'com')) %>%
  inner_join(com_names_bib %>% select(com, label, col), by = c('com_bib' = 'com')) %>%
  mutate(weight = 1) %>%
  rename(from = label.x,
         to = label.y) %>% # generic
  select(from, to, weight, col) %>% 
  drop_na() %>% 
  count(from, to, col, wt = weight, name = 'weight') %>%
  filter(percent_rank(weight) >= 0.25) %>%
  weight_jaccard(i = from, j = to, w = weight) %>% 
  select(-weight)

el_2m_topic <- M_top %>% select(UT, label) %>%
  left_join(M_bib %>% drop_na(com) %>% select(UT, label, col), by = 'UT') %>%
  rename(from = label.y,
         to = label.x) %>% # generic
  select(from, to, col) %>% 
  drop_na() %>% 
  count(from, to, col,  name = 'weight') %>%
  filter(percent_rank(weight) >= 0.25) %>%
  weight_jaccard(i = from, j = to, w = weight) %>% select(-weight)

# graph
g_3m <- el_2m_kb %>% 
  bind_rows(el_2m_topic) %>%
  as_tbl_graph(directed = TRUE) %N>%
  left_join(nl_3m, by = 'name') %>%
  mutate(
    level = case_when(
      type == "KB" ~ 1,
      type == "RA" ~ 2,
      type == "TP" ~ 3),
    coord_y = 0.1,
    coord_x = 0.001 + 1/(max(level)-1) * (level-1)
    )  %N>%
  filter(!is.na(level))
```

```{r, include=FALSE}
## Build sankey plot
fig <- plot_ly(type = "sankey", 
               orientation = "h",
               arrangement = "snap",
  node = list(
    label = g_3m %N>% as_tibble() %>% pull(name),
    x = g_3m %N>% as_tibble() %>% pull(coord_x),
    y = g_3m %N>% as_tibble() %>% pull(coord_y),
    color = g_3m %N>% as_tibble() %>% pull(col), 
    pad = 4
  ), 
  link = list(
    source = (g_3m %E>% as_tibble() %>% pull(from)) -1,
    target = (g_3m %E>% as_tibble() %>% pull(to)) -1,
    value =  g_3m %E>% as_tibble() %>% pull(weight_jac),
    color = g_3m %E>% as_tibble() %>% pull(col) %>% col2rgb() %>% as.matrix() %>% t() %>% as_tibble() %>% 
      mutate(col_rgb = paste0('rgba(', red, ',' , green, ',', blue, ',0.75)')) %>%  pull(col_rgb)
    )
) %>% 
  layout(title = paste('Knowledge Bases, Research Areas & Topics:', var_inst, 'Field around ', var_dept, sep = ' '),
         margin = list(l = 50, r = 50, b = 100, t = 100, pad = 2)) 
```


## Joint Overview over Knowledge Bases, Research Areas, and Topics

This plot shows the connection of publications in the research areas to knowledge bases (by citations) and topics (by gamma, document-topic weight)

```{r, fig.height= 10, fig.width=15}
fig
```


<!-- ####################################################################################### -->
<!-- ####################################################################################### -->
<!-- ############################# NEXT PART ############################################### -->
<!-- ####################################################################################### -->
<!-- ####################################################################################### -->


```{r, include=FALSE}
rm(text_tidy, text_lda)
```




# Collaboration 

```{r}
el_inst <- readRDS(paste0('../../temp/el_inst_', str_to_lower(var_inst), '_', str_to_lower(var_dept), '.rds'))
```


```{r}
g_inst <- el_inst %>% as_tbl_graph(directed = FALSE) %E>%
  filter(weight >= cutof_edge_cit ) %N>%
  filter(!node_is_isolated())
```

## Collaboration network 

```{r, fig.height= 10, fig.width=15}
# get biggest component
components <- clusters(g_inst, mode="weak")
biggest_cluster_id <- which.max(components$csize)
vert_ids <- V(g_inst)[components$membership == biggest_cluster_id]
igraph::induced_subgraph(g_inst, vert_ids)

g_inst %N>% 
  mutate(cent = centrality_degree(weights = weight)) %>%
  filter(name == paste(var_inst, var_dept)  | rank(-cent) <= 100 ) %>%
  ggraph(layout = "fr") + 
  geom_edge_link(aes(width = weight,
                     #color = .N()$name[from] == paste(var_inst, var_dept) | .N()$name[from] == paste(var_inst, var_dept),
                     #filter = (weight >= weight  %>% quantile(0.01))
                     )
                 , alpha = 0.25)  + 
  geom_node_point(aes(size = cent), col = 'steelblue1')  + 
  geom_node_text(aes(label = name, 
                     size = cent,
                     filter = (cent >= cent  %>% quantile(0.25))), repel = TRUE) +
  #theme_graph(base_family = "Arial") +
  theme(legend.position = 'bottom') +
  scale_edge_width_continuous(range = c(0.5, 5))  +
  scale_edge_colour_manual(values = c("grey", "red"), name = '1st degree') +
  scale_size(range = c(0.5,10)) 
```


# Endnotes

```{r}
sessionInfo()
```
